Age-related changes in plant growth and traits

### 2015-12-16 Accessory_figs_2015_12.Rmd
accessory costs patterns

@@

@@

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(accessory_inv~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
```

@@

SummaryInd$prop_fruit <- SummaryInd$fruit_weight / SummaryInd$repro_inv

>>>>

```{r}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
SummaryInd$costs_for_seed <- SummaryInd$seed_count * SummaryInd$seedcosts
SummaryInd$costs_for_aborted <- SummaryInd$repro_inv - SummaryInd$costs_for_seed
plot(costs_for_seed ~ costs_for_aborted,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
SummaryInd$prop_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
plot(prop_aborted ~ age, data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="x")

plot(costs_for_seed ~ repro_inv,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
abline(0,1)

par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "costs_for_aborted"
yvar <- "costs_for_seed"

```{r}
par(mfrow=c(2,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
#total reproductive investment much stronger correlation with total weight 
win.metafile("figs2/best_correlate2.wmf", height=6, width=12)
plot

par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log(total_weight_0)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)

plot(repro_inv~total_weight_0,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log(total_weight_0)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
words.top.left.logxy(mod)

plot(prepollen_all_inv~total_weight_0,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log(total_weight_0)~log(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
words.top.left.logxy(mod)

dev.off()

plot(propagule_inv~total_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_inv)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)

plot(repro_inv~total_inv,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
words.top.left.logxy(mod)

plot(prepollen_all_inv~total_inv,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_inv)~log(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
words.top.left.logxy(mod)

#shift in accessory costs per seed with seed size
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
win.metafile("figs2/accessory_per_seed_vs_seed_size.wmf", height=6, width=6)
plot
plot(accessory_per_seed~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
summary(mod)
abline(log(5),1)
dev.off()

#each species follows its own linear trajectory, but species lines are offset from one another
#species with lower intercepts have greater benefit if seed count is metric that matters; species with higher intercept less disadvntaged is a few heavy seeds worth as much as many smaller seeds
win.metafile("figs2/accessory_per_seed_vs_prop_propagule.wmf", height=6, width=6)
plot
plot(accessory_per_seed~prop_propagule,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
dev.off()
```

plot(seed_count~accessory_per_seed,data=subset(SummarySpp[["mean"]],seed_count>1),col=col.spp(species),pch=16,log="xy")
```{r}
plot(accessory_per_seed~growth_leaf,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~growth_leaf,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(growth_leaf)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)

plot(prop_propagule~growth_leaf,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(prop_propagule~growth_leaf,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(growth_leaf)~log(prop_propagule),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)

plot(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
abline(log(5),1)

plot(prop_propagule~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(prop_propagule~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size)~log(prop_propagule),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)

plot(costs_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
```

plot(accessory_per_seed~prop_propagule,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~prop_propagule,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)

@@

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "age"
yvar <- "seedset"

data <- subset(SummaryInd,seedset>0&age>3)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(accessory_inv~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
plot(accessory_per_seed~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
plot(propagule_inv~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(propagule_inv~repro_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(propagule_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(repro_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
abline(0,1)
```

@@

```{r}
SummaryInd$prop_fruit <- SummaryInd$fruit_weight / SummaryInd$repro_inv

SummaryInd$costs_for_seeds_produced <- SummaryInd$costs_per_seed*SummaryInd$seed_count
SummaryInd$costs_for_aborted <- SummaryInd$repro_inv - SummaryInd$costs_for_seeds_produced

plot(costs_for_seeds_produced~costs_for_aborted,data=subset(SummaryInd,seed_count>0),log="xy",col=col.spp(species), pch=16)

par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
xvar <- "costs_for_aborted"
yvar <- "costs_for_seeds_produced"

data <- subset(SummaryInd,prop_propagule>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

plot(seedcosts~seed_size,data=subset(SummaryInd),log="xy",col=col.spp(species), pch=16)
plot(accessory_per_seed~seed_size,data=subset(SummaryInd),log="xy",col=col.spp(species), pch=16)

### 2015-12-16 Flowering_parts_charts.Rmd
accessory costs patterns

#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
#plot
#win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
#plot
par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
midpoints <- barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.accessory(barplot_data$accessory_part),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$accessory_part,pch=16, cex=1,bty="n",col=col.accessory(barplot_data$accessory_part))

#text(midpoints,(barplot_data_matrix), labels=barplot_data_matrix)
#dev.off()
```

>>>>

#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
#plot

win.metafile("figs2/accessory_cost_barplot.wmf", height=4, width=10)
plot
par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
midpoints <- barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.accessory(barplot_data$accessory_part),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$accessory_part,pch=16, cex=1,bty="n",col=col.accessory(barplot_data$accessory_part))

#text(midpoints,(barplot_data_matrix), labels=barplot_data_matrix)
dev.off()
```
